Followers Are Not Enough: A Multi-faceted Approach to Community Detection in Online Social Networks

### 2014-11-23 paper-postreview/conclusions.tex
Reviewed section 3.4

%Start of future work**
Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
\alert{maybe move the top 10 people here}
 Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. But we have seen in our study that the structural network only highlights one of many possible ways that users interact with online social media.
Thus, a na\"ive application of centrality measures to a structural network may be answering a different question than the one motivating influence detection. For example, a user exhibiting high closeness centrality based on the structural network may be able to make a message visible to most other users in a social network, but this does not mean that those other users are likely to respond to or propagate that message. The importance of correctly framing network measures of influence has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.

Based on our preliminary results, we conjecture that weighted generalizations of these centrality measures using transfer entropy might lead to better insights about who is actually influential in an online social network. In addition to exploring this phenomenon further, we plan to explore a broader selection of choices for both the transfer-entropy lag and tweet history time resolution. We believe that by doing an in-depth analysis of both of these parameters we can discover interesting activity-based communities that occur on much broader time scales.
%End of futre work**
  %based on methods for model selection~\cite{claeskens2008model}.

>>>>

%Start of future work**
Our findings may have important implications to a common problem in social network analysis: identification of influential individuals---but further work must be carried out.
%\alert{maybe move the top 10 people here}
Many network measures of influence are based on the various types of centrality (degree, betweenness, closeness, eigenvector, etc.)~\cite{newman2009networks}. Most centralities depend explicitly on the structure of the network under consideration. But we have seen in our study that the structural network only highlights one of many possible ways that users interact with online social media.
Thus, a na\"ive application of centrality measures to a structural network may be answering a different question than the one motivating influence detection. For example, a user exhibiting high closeness centrality based on the structural network may be able to make a message visible to most other users in a social network, but this does not mean that those other users are likely to respond to or propagate that message. The importance of correctly framing network measures of influence has been explored previously~\cite{kitsak2010identification}, and our work further highlights its importance.

Based on our preliminary results, we conjecture that weighted generalizations of these centrality measures using transfer entropy might lead to better insights about who is actually influential in an online social network. 
It is interesting to note for example that two of the Forbes ``Top 10 Social Media Influencers", happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories. While we do not believe this information theoretic measure can capture social influence in its entirety, 
% members, as categorized by transfer entropy. 
this suggests that this activity-based measure may be useful in finding influential members purely based on their temporal tweet history; even completely ignoring both tweet content and social status. However, a deeper analysis would need to be carried out to verify this finding.
In addition to exploring this phenomenon further, we plan to explore a broader selection of choices for both the transfer-entropy lag and tweet history time resolution. We believe that by doing an in-depth analysis of both of these parameters we can discover interesting activity-based communities that occur on much broader time scales.
%End of futre work**
  %based on methods for model selection~\cite{claeskens2008model}.
